---
title: "hw5"
author: "Nihan Gencerliler"
date: "11/9/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(rvest)
library(stringr)
library(purrr)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 16, 
  fig.height = 12,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

```{r}

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

replace_missing = function(original_values) {
  if (is.numeric(original_values))
   {new_values=replace_na(original_values, mean(original_values,na.rm = TRUE))}
  else 
  {new_values=replace_na(original_values, "virginica")}
  new_values
}

iris_without_missing = map_dfr(iris_with_missing, replace_missing)

head(iris_without_missing)

```

For numeric variables, you should fill in missing values with the mean of non-missing values
For character variables, you should fill in missing values with "virginica"

## Problem 2

This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

subject ID   arm   observations   time
Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between group

```{r}
#create vector of filenames
files_vec=list.files(path = "./data", full.names = TRUE) 
#create dataframe of filenames, subjectID, arm
files_wide=
  
  data_frame(filename=files_vec, subject_ID=str_sub(files_vec,-6,-5), arm=str_sub(files_vec,-10,-8)) %>%
  #create new variable that reads each file into a dataframe and unnest to get each subject's weekly 
  #observations in wide format
  mutate(file_contents = map(filename,read.csv)
  ) %>%
  unnest(file_contents)

#tidy the data to long format in order to create the plot

files_long=
  files_wide %>%
   pivot_longer(week_1:week_8,
               names_to="week",
               names_prefix="week_",
               values_to="observation") %>%
    group_by(week, arm) %>%
    summarize(observation=mean(observation))

files_long %>%
ggplot(aes(x=week,y=observation,group=arm,color=arm)) + geom_line(size=5)

```


